Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-08 Paper/Supplementary.tex
Add column for Python variable name to list of symbols table

\documentclass[preprint,12pt,TurnOnLineNumbers]{JASAnew}
\usepackage{longtable}

\usepackage{lineno}
\linenumbers

@@

\begin{longtable}{p{0.25\linewidth} p{0.75\linewidth}}
Symbol & Description\\

$\atan(y,x)$ & The four quadrant inverse tangent which returns values in the interval $[-\pi,\pi]$ , inclusive.\\
$\cw$ & Sound speed in water [$m s^{-1}$].\\
$\decfac(\stagesym)$ & Integer filter decimation factor [1].\\
$\dft_\ndft(x)$ & The discrete Fourier transform of length $\ndft$ of $x$.\\
FT & The continuous Fourier transform. \\
$\freqsym$ & Frequency [Hz].\\
$\fc$ & Frequency at centre of linear upsweep chirp pulse. Equivalent to $\fstart + \frac{|\fstop - \fstart|}{2}$ [Hz].\\
$\fn$ & Nominal operating frequency of a transducer [Hz].\\
$\fs$ & Analogue to digital sampling frequency [Hz].\\
$\fsdec$ & Decimated sampling frequency [Hz].\\
$\fstart$ & Start frequency of linear upsweep chirp pulse [Hz].\\
$\fstop$ & Stop frequency of linear upsweep chirp pulse [Hz].\\

$\gain(\along,\athw,\freqsym)$ & Transducer gain as a function of echo arrival angle in the beam and frequency [1].\\

$\gain(\along,\athw,\samplesymf)$ & Transducer gain as a function of echo arrival angle in the beam and frequency index [1].\\

$\gainzero(\freqsym)$ & Transducer gain along the main acoustic axis, i.e. $\gain(\along, \athw,\freqsym)$ where $\along = \athw = 0$ [1].\\

$\hfl(\genidxsym,\stagesym)$ & Complex valued receiving filter coefficients [1].\\

$\Im(x)$ & The imaginary part of $x$.\\

$\samplesymf$ & Sample index in frequency domain [1].\\

$\nchannels$ & Total number of transducer sectors/transceiver channels that are used to receive and process the acoustic signal [1].\\
$\nstages$ & Total number of filter stages [1].\\
$\nw$ & Number of samples used in the sliding Hanning window [1].\\
$\samplesymt$ & Sample index in time domain [1]\\

$\prxetf(\freqsym)$ & FT of the received electric power in a matched load for the signal from a single target at frequency $\freqsym$ [W].\\
$\prxetf(\samplesymf)$ & DFT of the received electric power in a matched load for the signal from a single target [W].\\
$\prxevf(\freqsym)$ & FT of the received electric power in a matched load for the signal from a volume at frequency $\freqsym$ [W].\\
$\prxevf(\samplesymf)$ & DFT of the received electric power in a matched load for the signal from a volume [W$\textrm{m}^2$].\\
$\prxe(\samplesymt)$  & Received electric power in a matched load [W].\\

$\ptxe$ & Transmitted electric power [W].\\
$\ptxauto(\samplesymt)$ & Square of the absolute value of the matched filter autocorrelation function [1].\\

$\Re(x)$ & The real part of $x$.\\
$\range$ & Distance from transducer [m].\\
$\rangeref$ & Reference distance [m]. \\
$\range(\samplesymt)$ & Distance from transducer [m].\\

$\mysp(\samplesymt)$  & Point scattering strength [dB re 1 $\textrm{m}^2$].\\
$\sv$  & Volume backscattering strength [dB re 1 $\textrm{m}^{-1}$].\\
$\sv(\freqsym)$ & Volume backscattering strength at frequency $\freqsym$ [dB re 1 $\textrm{m}^{-1}$].\\
$\sv(\samplesymt)$ & Volume backscattering strength at sample index $\samplesymt$ [dB re $\textrm{m}^{-1}$]\\

$\ts$ & Target strength [dB re 1 $\textrm{m}^2$].\\
$\ts(\freqsym)$ & Target strength at frequency $f$ [dB re 1 $\textrm{m}^2$].\\
$\ts(\samplesymf)$ & Target strength at frequency index $\samplesymf$ [dB re 1 $\textrm{m}^{2}$]\\

$\timesym$ &  Time [s].\\
$\tslide$ & Duration of sliding window for calculating volume backscattering strength [s].\\

$\channelsym$ & Channel number/transducer sector [1].\\
$u(\genidxsym)$ & The Heaviside step function [1]. \\
$V$ & Volume occupied by scattering targets [$\textrm{m}^3$].\\
$\stagesym$ & Filter stage [1].\\

$\hannw$ & The Hanning window function [1].\\
$\hannw(\genidxsym)$ & The Hanning window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$ [1].\\
$\hannwnorm(\genidxsym)$ & Normalised Hanning window [1].\\

$x^*$ & The complex conjugate of $x$.\\
$||x||$ & The $l^2$-norm of $x$, also known as the Euclidean norm.\\

$\ymfautof(\samplesymf)$ & Discrete Fourier transform (DFT) of the autocorrelation function for the matched filter [1].\\
$\ymfautoredf(\samplesymf)$ & DFT of the reduced autocorrelation function for the matched filter [1].\\
$\ypctargetf(\samplesymf)$ & DFT of the pulse compressed signal from a single target [V].\\
$\ypctargetnormf(\samplesymf)$ & DFT of the pulse compressed signal from a single target 
normalized by the DFT of the reduced autocorrelation function for the matched filter [Vm].\\
$\ypcvolumef(\samplesymf)$ & DFT of the pulse compressed signal from a volume. Compensated for spreading loss [Vm].\\
$\ypcvolumenormf(\samplesymf)$ & DFT of the pulse compressed signal from a single volume normalized by the DFT of the reduced autocorrelation function for the matched filter.  Compensated for spreading loss [V].\\

$\ymf(\samplesymt)$ & Matched filter. Signal used for pulse compression [1].\\
$\ymfauto(\samplesymt)$ & Autocorrelation function for the matched filter [1].\\
$\ymfautored(\samplesymt)$ & Reduced autocorrelation function for the matched filter [1].\\

$\ypc(\samplesymt)$ & Pulse compressed signal averaged over all transducer sectors [V].\\
$\ypc(\samplesymt, \channelsym) $ & Pulse compressed signal from channel $\channelsym$ [V].\\
$y_{\textrm{pc,aft}}(\samplesymt)$ & Pulse compressed signal from the aft transducer half [V].\\
$y_{\textrm{pc,fore}}(\samplesymt)$ & Pulse compressed signal from the forward transducer half [V].\\
$y_{\textrm{pc,port}}(\samplesymt)$ & Pulse compressed signal from the port transducer half [V].\\
$\ypcspread(\samplesymt)$ & Pulse compressed signal compensated for spherical spreading [Vm].\\
$y_{\textrm{pc,star}}(\samplesymt)$ & Pulse compressed signal from the starboard transducer half [V].\\
$\ypctarget(\samplesymt)$ & Pulse compressed signal from a single target [V].\\

$\yrx(\samplesymt,\channelsym)$ & Received digitised, bandpass filtered, decimated complex signal after the final filter stage, $\yrx(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,\nstages)$ [V].\\
$\yrx(\samplesymt,\channelsym,\stagesym)$ & Received digitised, bandpass filtered, decimated complex signal [V].\\
$\yrxa(\timesym)$ & Analogue acoustic signal received by the transducer [Pa].\\
$\yrxa(\timesym,\channelsym)$ & Analogue acoustic signal received by each transducer sector $\channelsym$ [Pa].\\
$\yrxe(\timesym,\channelsym)$ & Analogue electric signal received by each transceiver channel $\channelsym$ [V].\\

$\yrxorg(\samplesymt,\channelsym)$ & Received digitised signal before the bandpass filtering and decimation stages, $\yrxorg(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,0)$ [V].\\

$\ytx(\samplesymt)$ & Ideal transmitted signal generated from transmit signal properties [V].\\
$\ytxnorm(\samplesymt)$ & Ideal normalized transmitted signal generated from transmit signal properties [1].\\
$\ytxnorm(\samplesymt,\stagesym)$ & Ideal normalized transmitted signal generated from transmit signal properties after application of filter stage $\stagesym$ [1].\\

$\ytxa(\timesym)$ & Analogue acoustic transmit signal [Pa].\\

$\ytxe(\timesym)$ & Analogue electric transmit signal [V].\\

$y_\along(\samplesymt)$ & Electrical angle along the minor axis of the transducer (alongship when ship-mounted) [$^{\circ}$].\\
$y_\athw(\samplesymt)$ & Electrical angle along the major axis of the transducer (athwartship when ship-mounted) [$^{\circ}$].\\

$\zrxe$ & Receiver electric impedance [$\Omega$].\\
$\ztde$ & Transducer sector electric impedance [$\Omega$].\\

$\absorp(\freqsym)$  & Absorption coefficient at frequency $f$ [dB $\textrm{m}^{-1}$].\\
$\absorp(\samplesymf)$ & Absorption coefficient at frequency index $m$ [dB $\textrm{m}^{-1}$]\\
$\anglefalong$ & Conversion factor between phase difference in signals from the fore and aft transducer halves and the physical arrival angle of an echo [1].\\
$\anglefathw$ & Conversion factor between phase difference in signals from the port and starboard transducer halves and the physical arrival angle of an echo [1].\\
$\along$ & Angle coordinates along the minor axis of the transducer (alongship when ship-mounted) [$^\circ$].\\
$\along(\samplesymt)$ & Angle of arrival of target echo along the minor axis of the transducer (alongship when ship-mounted) [$^\circ$].\\
$\wlen$ &  Acoustic wavelength [m].\\
$\wlen_\samplesymf$ & Acoustic wavelength at frequency index $m$ [m]\\
$\sigmabs$ & Backscattering cross-section [$\textrm{m}^2$].\\
$\tnom$ & Nominal transmit pulse duration [s].\\
$\teff$ & Effective transmit pulse duration [s].\\
$\athw$ & Angle coordinates along the major axis of the transducer (athwartship when ship-mounted) [$^\circ$].\\
$\athw(\samplesymt)$ & Angle of arrival of target echo along the major axis of the transducer (athwartship when ship-mounted) [$^\circ$].\\
$\eqang(\freqsym)$ & Two-way equivalent beam angle at frequency $\freqsym$ [sr].\\
\end{longtable}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{longtable}
\usepackage[landscape]{geometry}

@@

\begin{longtable}{p{0.15\linewidth} p{0.2\linewidth} p{0.65\linewidth} }
Symbol & Variable name & Description \\

$\atan(y,x)$ & & The four quadrant inverse tangent which returns values in the interval $[-\pi,\pi]$ , inclusive.\\
$\cw$ & & Sound speed in water [$m s^{-1}$].\\
$\decfac(\stagesym)$ & & Integer filter decimation factor [1].\\
$\dft_\ndft(x)$ & & The discrete Fourier transform of length $\ndft$ of $x$.\\
FT & n/a & The continuous Fourier transform. \\
$\freqsym$ & & Frequency [Hz].\\
$\fc$ & & Frequency at centre of linear upsweep chirp pulse. Equivalent to $\fstart + \frac{|\fstop - \fstart|}{2}$ [Hz].\\
$\fn$ & & Nominal operating frequency of a transducer [Hz].\\
$\fs$ & & Analogue to digital sampling frequency [Hz].\\
$\fsdec$ & & Decimated sampling frequency [Hz].\\
$\fstart$ & & Start frequency of linear upsweep chirp pulse [Hz].\\
$\fstop$ & & Stop frequency of linear upsweep chirp pulse [Hz].\\

$\gain(\along,\athw,\freqsym)$ & & Transducer gain as a function of echo arrival angle in the beam and frequency [1].\\

$\gain(\along,\athw,\samplesymf)$ & & Transducer gain as a function of echo arrival angle in the beam and frequency index [1].\\

$\gainzero(\freqsym)$ & & Transducer gain along the main acoustic axis, i.e. $\gain(\along, \athw,\freqsym)$ where $\along = \athw = 0$ [1].\\

$\hfl(\genidxsym,\stagesym)$ & & Complex valued receiving filter coefficients [1].\\

$\Im(x)$ & & The imaginary part of $x$.\\

$\samplesymf$ & & Sample index in frequency domain [1].\\

$\nchannels$ & & Total number of transducer sectors/transceiver channels that are used to receive and process the acoustic signal [1].\\
$\nstages$ & & Total number of filter stages [1].\\
$\nw$ & & Number of samples used in the sliding Hanning window [1].\\
$\samplesymt$ & & Sample index in time domain [1]\\

$\prxetf(\freqsym)$ & & FT of the received electric power in a matched load for the signal from a single target at frequency $\freqsym$ [W].\\
$\prxetf(\samplesymf)$ & & DFT of the received electric power in a matched load for the signal from a single target [W].\\
$\prxevf(\freqsym)$ & & FT of the received electric power in a matched load for the signal from a volume at frequency $\freqsym$ [W].\\
$\prxevf(\samplesymf)$ & & DFT of the received electric power in a matched load for the signal from a volume [W$\textrm{m}^2$].\\
$\prxe(\samplesymt)$  & & Received electric power in a matched load [W].\\

$\ptxe$ & & Transmitted electric power [W].\\
$\ptxauto(\samplesymt)$ & & Square of the absolute value of the matched filter autocorrelation function [1].\\

$\Re(x)$ & & The real part of $x$.\\
$\range$ & & Distance from transducer [m].\\
$\rangeref$ & & Reference distance [m]. \\
$\range(\samplesymt)$ & & Distance from transducer [m].\\

$\mysp(\samplesymt)$  & & Point scattering strength [dB re 1 $\textrm{m}^2$].\\
$\sv$  & & Volume backscattering strength [dB re 1 $\textrm{m}^{-1}$].\\
$\sv(\freqsym)$ & & Volume backscattering strength at frequency $\freqsym$ [dB re 1 $\textrm{m}^{-1}$].\\
$\sv(\samplesymt)$ & & Volume backscattering strength at sample index $\samplesymt$ [dB re $\textrm{m}^{-1}$]\\

$\ts$ & & Target strength [dB re 1 $\textrm{m}^2$].\\
$\ts(\freqsym)$ & & Target strength at frequency $f$ [dB re 1 $\textrm{m}^2$].\\
$\ts(\samplesymf)$ & & Target strength at frequency index $\samplesymf$ [dB re 1 $\textrm{m}^{2}$]\\

$\timesym$ & &  Time [s].\\
$\tslide$ & & Duration of sliding window for calculating volume backscattering strength [s].\\

$\channelsym$ & & Channel number/transducer sector [1].\\
$u(\genidxsym)$ & & The Heaviside step function [1]. \\
$V$ & & Volume occupied by scattering targets [$\textrm{m}^3$].\\
$\stagesym$ & & Filter stage [1].\\

$\hannw$ & & The Hanning window function [1].\\
$\hannw(\genidxsym)$ & & The Hanning window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$ [1].\\
$\hannwnorm(\genidxsym)$ & & Normalised Hanning window [1].\\

$x^*$ & & The complex conjugate of $x$.\\
$||x||$ & & The $l^2$-norm of $x$, also known as the Euclidean norm.\\

$\ymfautof(\samplesymf)$ & & Discrete Fourier transform (DFT) of the autocorrelation function for the matched filter [1].\\
$\ymfautoredf(\samplesymf)$ & & DFT of the reduced autocorrelation function for the matched filter [1].\\
$\ypctargetf(\samplesymf)$ & & DFT of the pulse compressed signal from a single target [V].\\
$\ypctargetnormf(\samplesymf)$ & & DFT of the pulse compressed signal from a single target 
normalized by the DFT of the reduced autocorrelation function for the matched filter [Vm].\\
$\ypcvolumef(\samplesymf)$ & & DFT of the pulse compressed signal from a volume. Compensated for spreading loss [Vm].\\
$\ypcvolumenormf(\samplesymf)$ & & DFT of the pulse compressed signal from a single volume normalized by the DFT of the reduced autocorrelation function for the matched filter.  Compensated for spreading loss [V].\\

$\ymf(\samplesymt)$ & & Matched filter. Signal used for pulse compression [1].\\
$\ymfauto(\samplesymt)$ & & Autocorrelation function for the matched filter [1].\\
$\ymfautored(\samplesymt)$ & & Reduced autocorrelation function for the matched filter [1].\\

$\ypc(\samplesymt)$ & & Pulse compressed signal averaged over all transducer sectors [V].\\
$\ypc(\samplesymt, \channelsym) $ & & Pulse compressed signal from channel $\channelsym$ [V].\\
$y_{\textrm{pc,aft}}(\samplesymt)$ & & Pulse compressed signal from the aft transducer half [V].\\
$y_{\textrm{pc,fore}}(\samplesymt)$ & & Pulse compressed signal from the forward transducer half [V].\\
$y_{\textrm{pc,port}}(\samplesymt)$ & & Pulse compressed signal from the port transducer half [V].\\
$\ypcspread(\samplesymt)$ & & Pulse compressed signal compensated for spherical spreading [Vm].\\
$y_{\textrm{pc,star}}(\samplesymt)$ & & Pulse compressed signal from the starboard transducer half [V].\\
$\ypctarget(\samplesymt)$ & & Pulse compressed signal from a single target [V].\\

$\yrx(\samplesymt,\channelsym)$ & & Received digitised, bandpass filtered, decimated complex signal after the final filter stage, $\yrx(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,\nstages)$ [V].\\
$\yrx(\samplesymt,\channelsym,\stagesym)$ & & Received digitised, bandpass filtered, decimated complex signal [V].\\
$\yrxa(\timesym)$ & & Analogue acoustic signal received by the transducer [Pa].\\
$\yrxa(\timesym,\channelsym)$ & & Analogue acoustic signal received by each transducer sector $\channelsym$ [Pa].\\
$\yrxe(\timesym,\channelsym)$ & & Analogue electric signal received by each transceiver channel $\channelsym$ [V].\\

$\yrxorg(\samplesymt,\channelsym)$ & & Received digitised signal before the bandpass filtering and decimation stages, $\yrxorg(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,0)$ [V].\\

$\ytx(\samplesymt)$ & & Ideal transmitted signal generated from transmit signal properties [V].\\
$\ytxnorm(\samplesymt)$ & & Ideal normalized transmitted signal generated from transmit signal properties [1].\\
$\ytxnorm(\samplesymt,\stagesym)$ & & Ideal normalized transmitted signal generated from transmit signal properties after application of filter stage $\stagesym$ [1].\\

$\ytxa(\timesym)$ & & Analogue acoustic transmit signal [Pa].\\

$\ytxe(\timesym)$ & & Analogue electric transmit signal [V].\\

$y_\along(\samplesymt)$ & & Electrical angle along the minor axis of the transducer (alongship when ship-mounted) [$^{\circ}$].\\
$y_\athw(\samplesymt)$ & & Electrical angle along the major axis of the transducer (athwartship when ship-mounted) [$^{\circ}$].\\

$\zrxe$ & & Receiver electric impedance [$\Omega$].\\
$\ztde$ & & Transducer sector electric impedance [$\Omega$].\\

$\absorp(\freqsym)$  & & Absorption coefficient at frequency $f$ [dB $\textrm{m}^{-1}$].\\
$\absorp(\samplesymf)$ & & Absorption coefficient at frequency index $m$ [dB $\textrm{m}^{-1}$]\\
$\anglefalong$ & & Conversion factor between phase difference in signals from the fore and aft transducer halves and the physical arrival angle of an echo [1].\\
$\anglefathw$ & & Conversion factor between phase difference in signals from the port and starboard transducer halves and the physical arrival angle of an echo [1].\\
$\along$ & & Angle coordinates along the minor axis of the transducer (alongship when ship-mounted) [$^\circ$].\\
$\along(\samplesymt)$ & & Angle of arrival of target echo along the minor axis of the transducer (alongship when ship-mounted) [$^\circ$].\\
$\wlen$ & &  Acoustic wavelength [m].\\
$\wlen_\samplesymf$ & & Acoustic wavelength at frequency index $m$ [m]\\
$\sigmabs$ & & Backscattering cross-section [$\textrm{m}^2$].\\
$\tnom$ & & Nominal transmit pulse duration [s].\\
$\teff$ & & Effective transmit pulse duration [s].\\
$\athw$ & & Angle coordinates along the major axis of the transducer (athwartship when ship-mounted) [$^\circ$].\\
$\athw(\samplesymt)$ & & Angle of arrival of target echo along the major axis of the transducer (athwartship when ship-mounted) [$^\circ$].\\
$\eqang(\freqsym)$ & & Two-way equivalent beam angle at frequency $\freqsym$ [sr].\\
\end{longtable}
